### 2022-05-08 ANA-TOPQ-2019-17-PAPER-metadata.tex
minor update
adding Attilio's comments for CONF note
update Luca's comments
update ATLAS-CONF-2022-014

%-------------------------------------------------------------------------------
% This file contains the title, author and abstract.
% It also contains all relevant document numbers used by the different cover pages.
%-------------------------------------------------------------------------------
% Title
%\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
\AtlasTitle{Search for flavour-changing neutral current interactions of the top quark and the Higgs
boson in events with a pair of $\tau$-leptons in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.10em}}
% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{1.1}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, an up-type quark ($q=u, c$), and a
Standard Model (SM) Higgs boson decaying into a $\tau$-lepton pair ($H\rightarrow \tau^+\tau^-$) is presented.
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
Large Hadron Collider that corresponds to an integrated luminosity of 139 fb$^{-1}$.
Two processes are considered:  single top quark FCNC production in association with a Higgs boson ($pp\rightarrow tH$), and top quark pair production in
which one of top quarks decays into $Wb$ and the other decays into $qH$ through the FCNC interactions.
The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ 
with an additional lepton (e,$\mu$),
as well as multiple jets. Event kinematics are used to separate signal from the background through a multivariate discriminant.  
A slight excess of data is observed above the expected SM background with a significance of 2.3$\sigma$,
and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.9 \times 10^{-4}$ ($5.0^{+2.2}_{-1.4}\times 10^{-4}$) and $7.2\times 10^{-4}$ ($3.6^{+1.7}_{-1.0}\times 10^{-4}$), respectively. 
The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.}%for the new physics scale $\Lambda$ at 1~TeV, respectively.} 
%$|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.%}
% Author - this does not work with revtex (add it after \begin{document})
%\author{The ATLAS Collaboration}

% ATLAS reference code, to help ATLAS members to locate the paper
\AtlasRefCode{TOPQ-2019-17}
%\AtlasRefCode{ATLAS-CONF-2018-049}

@@

% Comment deadline
\AtlasCoverCommentsDeadline{9 March 2022}

>>>>

%-------------------------------------------------------------------------------
% This file contains the title, author and abstract.
% It also contains all relevant document numbers used by the different cover pages.
%-------------------------------------------------------------------------------
% Title
%\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
\AtlasTitle{Search for flavour-changing neutral current interactions of the top quark and the Higgs
boson in events with a pair of $\tau$-leptons in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.10em}}
% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{1.4}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, an up-type quark ($q=u, c$), and a
Standard Model (SM) Higgs boson decaying into a $\tau$-lepton pair ($H\rightarrow \tau^+\tau^-$) is presented.
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
Large Hadron Collider that corresponds to an integrated luminosity of 139 fb$^{-1}$.
Two processes are considered:  single top quark FCNC production in association with a Higgs boson ($pp\rightarrow tH$), and top quark pair production in
which one of top quarks decays into $Wb$ and the other decays into $qH$ through the FCNC interactions.
The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ 
with an additional lepton (e,$\mu$),
as well as multiple jets. Event kinematics are used to separate signal from the background through a multivariate discriminant.  
A slight excess of data is observed above the expected SM background with a significance of 2.3$\sigma$,
and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.4 \times 10^{-4}\, (4.8^{+2.2}_{-1.4}\times 10^{-4})$
and $6.9\times 10^{-4}\, (3.5^{+1.5}_{-1.0}\times 10^{-4})$, respectively. 
The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
the effective $tqH$ couplings are $C_{c\phi} <1.35\, (0.97)$ and $C_{u\phi} <1.16\, (0.82)$, respectively.}%for the new physics scale $\Lambda$ at 1~TeV, respectively.} 
%$|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.%}
% Author - this does not work with revtex (add it after \begin{document})
%\author{The ATLAS Collaboration}

% ATLAS reference code, to help ATLAS members to locate the paper
%\AtlasRefCode{CONF-TOPQ-2022-06}
\AtlasRefCode{TOPQ-2019-17}
%\AtlasRefCode{ATLAS-CONF-2022-014}

@@

% Comment deadline
\AtlasCoverCommentsDeadline{9 May 2022}

### 2022-05-08 sections/background_estimation.tex
update to V1.3

In the leptonic channels, the events with prompt electron or muon and fake taus are modelled by calibrating MC with scale factors (SF)
derived from the dedicated $t\bar t$
control regions (CRtt) using dileptonic decays of $t\bar t$ events and semileptonic decays of $t\bar t$ events with two
$b$-jets, summarized in Table~\ref{tab:srcr}. 	
%the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
%aimed at fake taus from different origins.
There are four kinds of fake taus that need to be calibrated: Type-1 fake taus from hadronic $W$ boson decay ($\tau_{W}$) %$W$-jets ($\tau_{W}$)
with opposite-sign (OS) of charge to the light lepton;
Type-2 $\tau_{W}$'s with same-sign (SS) charge to the light lepton; Type-3 fake taus originating from $b$-hadron decays; Type-4 fake taus from light-flavour hadron decays.
The control regions are defined similar to the signal regions but with an additional $b$-jet or light lepton.
%$t_{\ell}t_{\ell}1b\thad$, $t_{\ell}t_{\ell}2b\thad$, $t_{\ell}t_h2b\thad$-2jSS, $t_{\ell}t_h2b\thad$-2jOS, $t_{\ell}t_h2b\thad$-3jSS, and $t_{\ell}t_h2b\thad$-3jOS.
The dilepton regions ($t_{\ell}t_{\ell}1b\thad$ and $t_{\ell}t_{\ell}2b\thad$) are used to calibrate Type-3 and Type-4 fake taus. The semileptonic
regions ($t_{\ell}t_h2b\thad$-2jOS and $t_{\ell}t_h2b\thad$-3jOS) where $\thad$ and light lepton have opposite charge are used to calibrate Type-1 fake taus.
Similarly for Type-2, the semileptonic regions ($t_{\ell}t_h2b\thad$-2jSS and $t_{\ell}t_h2b\thad$-3jSS) where $\thad$ and light lepton have same charge are used.
A simultaneous fit to data is made to derive the scale factors for fake taus in MC, which consist of total of 24 parameters
depending on four types, three $\pt$ bins, two bins for 1- and 3-prong taus separately.
The values of these scale factors range from 0.3-1.28 are then used to correct the MC estimated fakes in the corresponding  signal regions with a single $b$-jet.
In the $t_{\ell}\thadhad$ channel, both taus can be misidentified, so the calibration is applied to each tau separately, following the same procedure used in the $\tlhad$ channel.
%using the lepton and fake tau charges, then the scale factors are multiplied together.
The nominal value of scale factors will vary according to their uncertainties in the final fit. A closure test is made for the fake tau estimations using the same procedure
in the $t_{\ell}\thadhad$-SS validation region, which shows a good agreement between data and the background prediction. 
%In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated
%control regions discussed in Section~\ref{sec:strategy_Htautau}.

>>>>

In the leptonic channels, the events with prompt electron or muon and fake taus are modelled by calibrating MC with scale factors (SF)
derived from the dedicated $t\bar t$
control regions (CRtt) using dileptonic decays of $t\bar t$ events and semileptonic decays of $t\bar t$ events with two
$b$-jets, summarized in Table~\ref{tab:srcr}. 	
%the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
%aimed at fake taus from different origins.
There are four kinds of fake taus that need to be calibrated: Type-1 fake taus from hadronic $W$ boson decay ($\tau_{W}$) %$W$-jets ($\tau_{W}$)
with opposite-sign (OS) of charge to the light lepton;
Type-2 $\tau_{W}$'s with same-sign (SS) charge to the light lepton; Type-3 fake taus originating from $b$-hadron decays; Type-4 fake taus from light-flavour hadron decays.
The control regions are defined similar to the signal regions but with an additional $b$-jet or light lepton.
%$t_{\ell}t_{\ell}1b\thad$, $t_{\ell}t_{\ell}2b\thad$, $t_{\ell}t_h2b\thad$-2jSS, $t_{\ell}t_h2b\thad$-2jOS, $t_{\ell}t_h2b\thad$-3jSS, and $t_{\ell}t_h2b\thad$-3jOS.
The dilepton regions ($t_{\ell}t_{\ell}1b\thad$ and $t_{\ell}t_{\ell}2b\thad$) are used to calibrate Type-3 and Type-4 fake taus. The semileptonic
regions ($t_{\ell}t_h2b\thad$-2jOS and $t_{\ell}t_h2b\thad$-3jOS) where $\thad$ and light lepton have opposite charge are used to calibrate Type-1 fake taus.
Similarly for Type-2, the semileptonic regions ($t_{\ell}t_h2b\thad$-2jSS and $t_{\ell}t_h2b\thad$-3jSS) where $\thad$ and light lepton have same charge are used.
A simultaneous fit to data is made to derive the scale factors for fake taus in MC, which consist of a total of 24 parameters
depending on four types of fake taus, three $\pt$ bins, two bins for 1- and 3-prong taus separately. The post-fit distributions of the
leading $\thad$ $\pt$ and measured tau scale factors are presented in Appendix~\ref{sec:tauFF_appendix}. 
The values of these scale factors range from 0.3-1.28 are then used to correct the MC estimated fakes in the corresponding  signal regions with a single $b$-jet.
In the $t_{\ell}\thadhad$ channel, both taus can be misidentified, so the calibration is applied to each tau separately, following the same procedure used in the $\tlhad$ channel.
%using the lepton and fake tau charges, then the scale factors are multiplied together.
The nominal value of scale factors will vary according to their uncertainties in the final fit. A closure test is made for the fake tau estimations using the same procedure
in the $t_{\ell}\thadhad$-SS validation region, which shows a good agreement between data and the background prediction. 
%In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated
%control regions discussed in Section~\ref{sec:strategy_Htautau}.

### 2022-05-08 sections/objects.tex

Tight isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions based on a trained isolation boosted decision tree \texttt{PromptLeptonVeto}(PLIV), which is used to identify non-prompt light leptons using lifetime information associated with a track jet that matches the selected light lepton~\cite{ATLAS-CONF-2019-045}. These additional reconstructed charged particle tracks inside the jet can be
used to increase the accuracy for identifying the displaced decay vertex of heavy flavour (b, c) hadrons that produced non-prompt leptons.
The tight working points are used for high $\pt$ lepton ($>20~\GeV$).
The scale factors for the efficiencies of the tight \texttt{PLIV} working points are measured using the tag and probe method
with $Z\rightarrow \ell^+\ell^-$ events. These scale factors have also been checked for the electron or muon from the tau decay
using $Z\rightarrow\tau\tau\rightarrow e\mu4\nu$ samples, which is consistent at 2\% level. To be conservative, an
additional uncertainty of $\pm 2\%$ is considered for the PLIV efficiency for the tau-lepton in the lepton+$\thad$ channels.
%Additionally, the $\Htautau$ search requires leptons to
%satisfy a calorimeter-based isolation criterion; a requirement is made on the sum of the transverse energy of
%topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contribution
%from the energy deposit of the lepton itself and correcting for pile-up effects, to be less than a $\pt$-dependent 
%percentage of the lepton energy. 
%The combined efficiency of track-based and calorimeter-based isolation requirements made by the $\Htautau$ 
%search is 90\% (99\%) at $\pt=25\;(60)~\gev$.

%a Gradient isolation working points are used for both electrons and muons. The working points are based on cut maps derived from the $Z\to l^+l^-$ Monte Carlo samples. The efficiency maps are simply derived from the sum of transverse energy of the clusters deposited in the calorimeter in the given cone. The efficiency for the leptons with a certain $\pt$ is $(0.1143*\pt[\GeV]+92.14)\%*(0.1143*\pt[\GeV]+92.14)\%$.
%draft 1 version
%Candidate jets are reconstructed with the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2005hq,Cacciari:2011ma} with a
%radius parameter $R=0.4$, using topological clusters~\cite{Aad:2016upy} 
%built from energy deposits in the calorimeters calibrated to the electromagnetic scale. 
Candidate jets are reconstructed using the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2005hq} with a
radius parameter $R=0.4$ applied to topological energy clusters~\cite{Aad:2016upy} and charged-particle tracks, processed using
a particle-flow algorithm~\cite{Aad:2017epj77}. %newref Eur. Phys. J. C 77 (2017) 466
%as implemented in the \fastjet\ package~\cite{Cacciari:2011ma}.  
%Jet reconstruction in the calorimeter starts from topological clustering~\cite{Aad:2016upy} of individual calorimeter cells calibrated to the electromagnetic energy scale. 
The reconstructed jets are then calibrated to the particle level by the application of a jet energy scale 
derived from simulation and in situ corrections based on $\sqrt{s}=13~\tev$ data~\cite{Aaboud:2017jcu}. %(TBD: check PFlow jets description)
The calibrated jets used are required to have $\pt > 25~\gev$ and $|\eta| < 2.5$.
Jet four-momenta are corrected for pile-up effects using the jet-area method~\cite{Cacciari:2008gn}.

@@

Hadronically decaying $\tau$-lepton ($\had$) candidates are reconstructed from energy clusters in the calorimeters and
associated inner-detector tracks~\cite{ATL-PHYS-PUB-2019-033}. %newref
%~\cite{ATL-PHYS-PUB-2015-045}.
Candidates are required to have either one or three associated tracks,
with a total charge of $\pm 1$.
%Candidates are required to have \pt 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
A Recurrent Neural Network (RNN)~\cite{Graves:2012SCI}
%~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna}
%A. Graves, Supervised Sequence Labelling with Recurrent Neural Networks, Studies in Computational Intelligence 385, Springer, 2012.
using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject jet backgrounds.
Three working points labelled loose, medium and tight are defined, and correspond to different $\had$ identification efficiency values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the medium
working point for the nominal selection.
%, while the loose working point is used for background estimation.
The medium working point has a combined reconstruction and identification efficiency of 75\% (60\%) for one-prong (three-prong) $\had$ 
decays, and an expected rejection factor against light-jets of 35 (240)~\cite{ATL-PHYS-PUB-2019-033}. 
Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
Events with a $b$-tagged $\had$ candidate are rejected.
%(TBD: check RNN description and update then numbers)
%Overlaps between candidate objects are removed sequentially, following this order: muons, electrons,
%$\tauhad$ (only for the $\Htautau$ search), and jets. In the $\Hbb$ search, firstly, electron candidates that lie 
%within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
%Overlaps between electron and jet candidates are resolved next, and finally, overlaps between remaining jet candidates 
%and muon candidates are removed. Clusters from identified electrons are not excluded during jet reconstruction. 
%In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 
%is discarded. If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
%The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
%that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
%Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
%and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
%few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
%if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
%In the $\Htautau$ search, a fixed cone size of $\Delta R=0.2$ is used to determine the overlap between
%candidate objects, and only the highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the
%analysis channel, see Section~\ref{sec:data_presel}) are considered to resolve their overlap with jets.

>>>>

Tight isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions based on a trained isolation boosted decision tree \texttt{PromptLeptonVeto}(PLIV), which is used to identify non-prompt light leptons using lifetime information associated with a track jet that matches the selected light lepton~\cite{ATLAS-CONF-2019-045}. These additional reconstructed charged particle tracks inside the jet can be
used to increase the accuracy for identifying the displaced decay vertex of heavy flavour ($b$, $c$) hadrons that produced non-prompt leptons.
The tight working points are used for high $\pt$ lepton ($>20~\GeV$).
The scale factors for the efficiencies of the tight \texttt{PLIV} working points are measured using the tag and probe method
with $Z\rightarrow \ell^+\ell^-$ events. These scale factors have also been checked for the electron or muon from the tau decay
using $Z\rightarrow\tau\tau\rightarrow e\mu4\nu$ samples, which is consistent at 2\% level. To be conservative, an
additional uncertainty of $\pm 2\%$ is considered for the PLIV efficiency for the tau-lepton in the lepton+$\thad$ channels.
%Additionally, the $\Htautau$ search requires leptons to
%satisfy a calorimeter-based isolation criterion; a requirement is made on the sum of the transverse energy of
%topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contribution
%from the energy deposit of the lepton itself and correcting for pile-up effects, to be less than a $\pt$-dependent 
%percentage of the lepton energy. 
%The combined efficiency of track-based and calorimeter-based isolation requirements made by the $\Htautau$ 
%search is 90\% (99\%) at $\pt=25\;(60)~\gev$.

%a Gradient isolation working points are used for both electrons and muons. The working points are based on cut maps derived from the $Z\to l^+l^-$ Monte Carlo samples. The efficiency maps are simply derived from the sum of transverse energy of the clusters deposited in the calorimeter in the given cone. The efficiency for the leptons with a certain $\pt$ is $(0.1143*\pt[\GeV]+92.14)\%*(0.1143*\pt[\GeV]+92.14)\%$.
%draft 1 version
%Candidate jets are reconstructed with the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2005hq,Cacciari:2011ma} with a
%radius parameter $R=0.4$, using topological clusters~\cite{Aad:2016upy} 
%built from energy deposits in the calorimeters calibrated to the electromagnetic scale. 
Candidate jets are reconstructed using the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2005hq} with a
radius parameter $R=0.4$ applied to topological energy clusters~\cite{Aad:2016upy} and charged-particle tracks, processed using
a particle-flow algorithm~\cite{Aad:2017epj77}. %newref Eur. Phys. J. C 77 (2017) 466
%as implemented in the \fastjet\ package~\cite{Cacciari:2011ma}.  
%Jet reconstruction in the calorimeter starts from topological clustering~\cite{Aad:2016upy} of individual calorimeter cells calibrated to the electromagnetic energy scale. 
The reconstructed jets are then calibrated to the particle level by the application of a jet energy scale 
derived from simulation and in situ corrections based on $\sqrt{s}=13~\tev$ data~\cite{Aaboud:2017jcu}. %(TBD: check PFlow jets description)
The calibrated jets used are required to have $\pt > 25~\gev$ and $|\eta| < 2.5$.
The four-momentum of the jets is corrected for pile-up effects using the jet-area method~\cite{Cacciari:2008gn}.

@@

Hadronically decaying $\tau$-lepton ($\had$) candidates are reconstructed from energy clusters in the calorimeters and
associated inner-detector tracks~\cite{ATL-PHYS-PUB-2019-033}. %newref
%~\cite{ATL-PHYS-PUB-2015-045}.
Candidates are required to have either one or three associated tracks,
with a total charge of $\pm 1$.
%Candidates are required to have \pt 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
A Recurrent Neural Network (RNN)~\cite{Graves:2012SCI}
%~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna}
%A. Graves, Supervised Sequence Labelling with Recurrent Neural Networks, Studies in Computational Intelligence 385, Springer, 2012.
using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject jet backgrounds.
Three working points labelled loose, medium and tight are defined, and correspond to different $\had$ identification efficiency values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the medium
working point for the nominal selection.
%, while the loose working point is used for background estimation.
The medium working point has a combined reconstruction and identification efficiency of 75\% (60\%) for one-prong (three-prong) $\had$ 
decays, and an expected rejection factor against light-jets of 35 (240)~\cite{ATL-PHYS-PUB-2019-033}. 
Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
Events are rejected if the jet seeding the $\had$ candidate is $b$-tagged.
%Events with a $b$-tagged  $\had$ candidate are rejected.
%(TBD: check RNN description and update then numbers)
%Overlaps between candidate objects are removed sequentially, following this order: muons, electrons,
%$\tauhad$ (only for the $\Htautau$ search), and jets. In the $\Hbb$ search, firstly, electron candidates that lie 
%within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
%Overlaps between electron and jet candidates are resolved next, and finally, overlaps between remaining jet candidates 
%and muon candidates are removed. Clusters from identified electrons are not excluded during jet reconstruction. 
%In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 
%is discarded. If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
%The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
%that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
%Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
%and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
%few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
%if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
%In the $\Htautau$ search, a fixed cone size of $\Delta R=0.2$ is used to determine the overlap between
%candidate objects, and only the highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the
%analysis channel, see Section~\ref{sec:data_presel}) are considered to resolve their overlap with jets.

### 2022-05-08 sections/statistical_analysis.tex
minor update for the final confnote

The final discriminant distributions are the BDT outputs of all the considered analysis regions. They are jointly analysed to test for the 
presence of a signal. The BDT distributions are binned to maximize the signal sensitivity.
The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $tH$ and $tt(qH)$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$,
and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations. 
Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
All nuisance parameters are subject to Gaussian constraints in the likelihood.
For a given value of $\mu$, the nuisance parameters $\theta$ allow variations of the expectations for signal and background
according to the corresponding systematic uncertainties, and their fitted values result in the deviations from
the nominal expectations that globally provide the best fit to the data.
This procedure allows a reduction of the impact of systematic uncertainties on 
the search sensitivity by taking advantage of the highly populated background-dominated bins included in the likelihood fit.
%To verify the improved background prediction, fits under the background-only hypothesis are performed, 
%and differences between the data and the post-fit background prediction are checked 
%using kinematic variables other than the ones used in the fit. 
Statistical uncertainties in each bin of the predicted final discriminant distributions are taken into account by dedicated parameters in the fit.     
The best-fit $\BR(t\to qH)$ is obtained by performing a binned likelihood fit to the data under the signal-plus-background
hypothesis, maximising the likelihood function ${\cal L}(\mu,\theta)$ over $\mu$ and $\theta$.

@@

%In the absence of signal,
Exclusion limits are set on $\mu$ , and thus on
$\BR(t\to qH)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of the $\BR(t\to qH)$ yielding CL$_{\textrm{s}} < 0.05$,
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

>>>>

The final discriminant distributions are the BDT outputs of all the considered analysis regions. They are jointly analysed to test for the 
presence of a signal. The BDT distributions are binned to maximize the signal sensitivity.
The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $tH$ and $tt(qH)$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$,
and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations.
The $pp\rightarrow tH$ production cross section is related to $\BR(t\rightarrow qH)$ based on their dimension-6 operators~\cite{fcnc_production_theory}.
Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
All nuisance parameters are subject to Gaussian constraints in the likelihood.
For a given value of $\mu$, the nuisance parameters $\theta$ allow variations of the expectations for signal and background
according to the corresponding systematic uncertainties, and their fitted values result in the deviations from
the nominal expectations that globally provide the best fit to the data.
This procedure allows a reduction of the impact of systematic uncertainties on 
the search sensitivity by taking advantage of the highly populated background-dominated bins included in the likelihood fit.
%To verify the improved background prediction, fits under the background-only hypothesis are performed, 
%and differences between the data and the post-fit background prediction are checked 
%using kinematic variables other than the ones used in the fit. 
Statistical uncertainties in each bin of the predicted final discriminant distributions are taken into account by dedicated parameters in the fit.     
The best-fit $\BR(t\to qH)$ is obtained by performing a binned likelihood fit to the data under the signal-plus-background
hypothesis, maximising the likelihood function ${\cal L}(\mu,\theta)$ over $\mu$ and $\theta$.

@@

%In the absence of signal,
Exclusion limits are set on $\mu$ and thus on
$\BR(t\to qH)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of the $\BR(t\to qH)$ yielding CL$_{\textrm{s}} < 0.05$,
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

### 2022-05-08 sections/tau_FF_appendix.tex

Figure~\ref{fig:ttCR_mtt} shows the post-fit of the leading $\thad$ $\pt$ in the ttCRs, which shows a good agreement between the data and the fitted background model.
Table~\ref{tab:ff1_summary} and~\ref{tab:ff2_summary} are summarized the fake scale factors of 1-prong and 3-prong taus
derived from the ttCRs including both statistical and systematic uncertainties.

@@

\begin{table}
\caption{ Summary of fake tau (1-prong) scale factors derived in the ttCRs. The numbers are shown as: nominal values, statistical, and systematics erros. }
\begin{center}
\begin{tabular}{lcccccc}
\toprule\toprule

>>>>

Figure~\ref{fig:ttCR_mtt} presents the post-fit distributions of the leading $\thad$ $\pt$ in the ttCRs, which shows a good agreement between the data and the fitted background model.
Table~\ref{tab:ff1_summary} and~\ref{tab:ff2_summary} summarize the fake scale factors of 1-prong and 3-prong taus
derived from the ttCRs including both statistical and systematic uncertainties.

@@

\begin{table}
\caption{ Summary of fake tau (1-prong) scale factors derived in the ttCRs. The numbers are shown as: nominal values, statistical, and systematics uncertainties. }
\begin{center}
\begin{tabular}{lcccccc}
\toprule\toprule
